DeconvOptim.jl - Signal Deconvolution with Julia

### 2021-08-07 paper/paper.tex
Update paper [no ci]

\begin{abstract}

Deconvolution is a versatile method to enhance the quality of signals measured with systems which can 
be expressed mathematically as a convolution of a system's response function with a signal. 
In this paper, we present \verb|DeconvOptim.jl|, a flexible toolbox written in Julia to deconvolve one or multiple multi-dimensional signals which have been
degraded by a multi-dimensional signal response function. 
\verb|DeconvOptim.jl| works both on CPUs and GPUs and utilizes recent advancements in Julias automatic differentiation ecosystem.

@@

        \begin{table}[h]
            \begin{tabular}{l l l}
                &  CPU in s& GPU in s\\ 
            \hline
            \verb|DeconvOptim.jl| & 14.0 & 0.86\\
            \verb|DeconvOptim.jl| - TV & 18.9 & 1.55 \\
            Richardson-Lucy (Julia) & 14.8 & 1.26 \\
            \verb|ThreeDeconv.jl|& 2415 & 44.5 \\
            \verb|GenericDeconv|  & 127 & 5.9\\
            \verb|GenericDeconv| - TV & 213 & 8.7 \\
            \verb|Huygens|  & & \\
            \verb|DeconvolutionLab2| - LR & 1089 & \\
            \verb|DeconvolutionLab2| - LR TV& 1131 & 
            \end{tabular}
            \caption{Runtimes of different deconvolution implementations.}
            \label{tab:deconv}
        \end{table}

@@

        \begin{table}[h]
            \begin{tabular}{l l l}
                & Loss & iterations \\ 
            \hline
            \verb|DeconvOptim.jl| & Poisson & 15 \\
            \verb|DeconvOptim.jl| TV & Poisson & 15\\
            Richardson-Lucy & Poisson & 120 \\
            \verb|ThreeDeconv.jl|  & Gauss+Poisson& 500\\
            \verb|GenericDeconv|  & Poisson & 40\\
            \verb|GenericDeconv| TV & Poisson & 40 \\
            \verb|Huygens|  & & \\
            \verb|DeconvolutionLab2| LR & Poisson & 200\\
            \verb|DeconvolutionLab2| LR TV& Poisson & 200 
            \end{tabular}
            \caption{Overview which loss function (noise model) and number of iterations are used.}
            \label{tab:deconvprop}
        \end{table}

        As summary of those performance tests we can state that our Julia implementation is very competitive and especially on the CPU it is only
        beaten by the commercial \verb|Huygens| software. Despite \verb|ThreeDeconv.jl| written in Julia 
        it is notably slower in comparison to our implementation.
        \verb|DeconvolutionLab2| is written in Java and uses hand optimized gradients but still its speed is comparably poor.
        \begin{figure}[h]
            \begin{subfigure}{.3\textwidth}
                \centering
                \includegraphics[width=\textwidth]{figures/DeconvOptim_cuda_no_regularizer_0.87s.png}
                \caption{\texttt{DeconvOptim.jl} without regularizer}
            \end{subfigure}
            \begin{subfigure}{.3\textwidth}
                \centering
                \includegraphics[width=\textwidth]{figures/DeconvOptim_TV_0.002.png}
                \caption{\texttt{DeconvOptim.jl} with TV}
            \end{subfigure}
            \begin{subfigure}{.3\textwidth}
                \centering
                \includegraphics[width=\textwidth]{figures/Lucy_richardson_julia.png}
                \caption{\texttt{DeconvOptim.jl} Richardson-Lucy}
            \end{subfigure}
            \begin{subfigure}{.3\textwidth}
                \centering
                \includegraphics[width=\textwidth]{figures/Deconvolution_Lab2_200iterations.PNG}
                \caption{\texttt{Deconvolution\\Lab2} with TV}
            \end{subfigure}
            \begin{subfigure}{.3\textwidth}
                \centering
                \includegraphics[width=\textwidth]{figures/ThreeDeconv_600_iterations.png}
                \caption{\texttt{ThreeDeconv.jl}}
            \end{subfigure}
            \begin{subfigure}{.3\textwidth}
                \centering
                \includegraphics[width=\textwidth, height=2.5cm]{example-image-a}
                \caption{\texttt{GenericDeconv}}
            \end{subfigure}
            \begin{subfigure}{.3\textwidth}
                \centering
                \includegraphics[width=\textwidth, height=2.5cm]{example-image-a}
                \caption{\texttt{Huygens}}
            \end{subfigure}
            \begin{subfigure}{.3\textwidth}
                \centering
                \includegraphics[width=\textwidth]{figures/noisy.png}
                \caption{~~Measured image with Poisson noise}
            \end{subfigure}
            \caption{Overview of some of the deconvolution results of different packages.}
            \label{img:results}
        \end{figure}

@@

>>>>

\begin{abstract}
\todo{fix citations with PkgCite.jl}
Deconvolution is a versatile method to enhance the quality of signals measured with systems which can 
be expressed mathematically as a convolution of a system's response function with a signal. 
In this paper, we present \verb|DeconvOptim.jl|, a flexible toolbox written in Julia to deconvolve one or multiple multi-dimensional signals which have been
degraded by a multi-dimensional signal response function. 
\verb|DeconvOptim.jl| works both on CPUs and GPUs and utilizes recent advancements in Julias automatic differentiation ecosystem.

@@

        \begin{table}[h]
            \begin{tabular}{l l l}
                &  CPU in s& GPU in s\\ 
            \hline
            \verb|DeconvOptim.jl| & 32.9 & 2.20\\
            \verb|DeconvOptim.jl| - TV & 39.9 & 4.46 \\
            Richardson-Lucy (Julia) & 40.0 & 3.05 \\
            \verb|ThreeDeconv.jl|& 1550 & 27.1 \\
            \verb|GenericDeconv|  & 140 & 6.32\\
            \verb|GenericDeconv| - TV & 233 & 9.35 \\
            \verb|Huygens| & 30.1 & 6.8 \\
            \verb|DeconvolutionLab2| - LR& 1640 & \\
            \end{tabular}
            \caption{Runtimes of different deconvolution implementations.}
            \label{tab:deconv}
        \end{table}

@@

        \begin{table}[h]
            \begin{tabular}{l l l}
                & Loss & iterations \\ 
            \hline
            \verb|DeconvOptim.jl| & Poisson & 45 \\
            \verb|DeconvOptim.jl| TV & Poisson & 45\\
            Richardson-Lucy & Poisson & 300 \\
            \verb|ThreeDeconv.jl|  & Gauss+Poisson& 300\\
            \verb|GenericDeconv|  & Poisson & 45\\
            \verb|GenericDeconv| TV & Poisson & 45 \\
            \verb|Huygens| & & \\
            \verb|DeconvolutionLab2| LR & Poisson & 300\\
            \verb|DeconvolutionLab2| LR TV& Poisson & 300 
            \end{tabular}
            \caption{Overview which loss function (noise model) and number of iterations are used.}
            \label{tab:deconvprop}
        \end{table}
        As summary of those performance tests we can state that our Julia implementation is very competitive and especially on the GPU
        it was the fastest of the tested packages. On the CPU it is only beaten by the commercial \verb|Huygens| software. 
        Despite \verb|ThreeDeconv.jl| written in Julia it is notably slower in comparison to our implementation.
        \verb|DeconvolutionLab2| is written in Java and uses hand optimized gradients but still its speed is poor.

        \todo{maximum intensity}
        \begin{figure}[h]
            \centering
            \begin{subfigure}{.3\textwidth}
                \centering
                \includegraphics[width=\textwidth]{figures/MIPs/mip_DeconvOptim.png}
                \caption{\texttt{DeconvOptim.jl} . $\text{NCC}= 0.86$.}
            \end{subfigure}
            \begin{subfigure}{.3\textwidth}
                \centering
                \includegraphics[width=\textwidth]{figures/MIPs/mip_DeconvOptim_RL.png}
                \caption{Julia Richardson-Lucy. $\text{NCC}= 0.74$.}
            \end{subfigure}
            \begin{subfigure}{.3\textwidth}
                \centering
                \includegraphics[width=\textwidth]{figures/MIPs/mip_DeconvolutionLab2.png}
                \caption{\texttt{Deconvolution Lab2}. $\text{NCC}= 0.76$.}
            \end{subfigure}
            \begin{subfigure}{.3\textwidth}
                \centering
                \includegraphics[width=\textwidth]{figures/MIPs/mip_ThreeDeconv.png}
                \caption{\texttt{ThreeDeconv.jl}. $\text{NCC}= 0.85$.}
            \end{subfigure}
            \begin{subfigure}{.3\textwidth}
                \centering
                \includegraphics[width=\textwidth]{figures/MIPs/mip_GenericDeconv.png}
                \caption{\texttt{GenericDeconv}. $\text{NCC}= 0.86$.}
            \end{subfigure}
            \begin{subfigure}{.3\textwidth}
                \centering
                \includegraphics[width=\textwidth]{figures/MIPs/mip_Huygens.png}
                \caption{\texttt{Huygens}$\text{NCC}= 0.86$.}
            \end{subfigure}
            \begin{subfigure}{.3\textwidth}
                \centering
                \includegraphics[width=\textwidth]{figures/MIPs/mip_raw.png}
                \caption{Measured image. $\text{NCC}= 0.41$.}
            \end{subfigure}
            \begin{subfigure}{.3\textwidth}
                \centering
                \includegraphics[width=\textwidth]{figures/MIPs/mip_ground_truth.png}
                \caption{Ground truth. $\text{NCC}= 1.0$}
            \end{subfigure}
            \caption{Overview of some of the deconvolution results of different packages.}
            \label{img:results}
        \end{figure}

@@

\section{Acknowledgement}
This work was partially funded by the Honours Programme of the Friedrich Schiller 
University of Jena\footnote{\url{https://www.uni-jena.de/en/honours_programme}}. 
Additionally, we want to thank Scientific Volume Imaging for providing a trial license for Huygens and especially Mark Koenis for advising
us how to adjust the settings to get optimal performance.
